### 2017-08-04 adjoint-model.tex
EM symmetric proof; exchange comonadically proof

@@

  The first triangle in Definition~\ref{def:smcc} commutes as follows:
  (1)--coalgebra; (2)--$\varepsilon$ is monoidal; (3)--naturality of $\rho$; (4)--naturality of
  $\varepsilon$; (5)--naturality of $\m{}$; (6)--$F$ is monoidal; (7)--$\cat{C}$ is symmetric;
  (8)--naturality of $\e{}$; (9)--$G$ is monoidal.
  \begin{mathpar}
  \bfig
    \Vtriangle/->`=`/<800,800>[A\tri I'`FGA\tri FGI'`A\tri I';h_A\tri h_{I'}``]
    \Ctrianglepair(1600,0)|mmmmm|/->`<-``=`<-/<800,400>[
      FGA\tri FGI'`FGA\tri I'`FGA\tri FI`FGA\tri I';
      id_{FGA}\tri\varepsilon_{I'}`id_{FGA}\tri F\n{I'}```id_{FGA}\tri\m{I}]
    \morphism(800,400)|m|<0,-400>[FGA\tri I'`A\tri I';\varepsilon_{FGA}\tri id_{I'}]
    \morphism(1600,400)|m|<800,0>[FGA\tri FI`F(GA\otimes I);\m{GA,I}]
    \morphism(1600,0)|m|<0,-400>[FGA\tri I'`FGA;\rho_{FGA}']
    \dtriangle(1600,-400)|mmm|/->`->`<-/<800,800>[
      F(GA\otimes I)`FGA`F(I\otimes GA);
      F\rho_{GA}`F\e{GA,I}`F\lambda_{GA}]
    \square(1600,-800)/->``->`<-/<1600,1600>[
      FGA\tri FGI'`F(GA\otimes GI')`FG(I'\tri A)`F(GI'\otimes GA);
      \m{GA,GI'}``F\e{GA,GI'}`F\n{I',A}]
    \morphism(2400,400)|m|<800,400>[F(GA\otimes I)`F(GA\otimes GI');F(id_{GA}\otimes\n{I'})]
    \morphism(2400,-400)|m|<800,-400>[F(I\otimes GA)`F(GI'\otimes GA);F(\n{I'}\otimes id_{GA})]
    \morphism(0,800)|l|<0,-1200>[A\tri I'`A;\rho_A']
    \square(0,-800)|mlmb|/<-`->`<-`<-/<1600,400>[
      A`FGA`I'\tri A`FG(I'\tri A);\varepsilon_A`\lambda_A'`FG\lambda_A'`\varepsilon_{I'\tri A}]
    \morphism(800,600)//<0,0>[`;(1)]
    \morphism(1300,400)//<0,0>[`;(2)]
    \morphism(800,-200)//<0,0>[`;(3)]
    \morphism(800,-600)//<0,0>[`;(4)]
    \morphism(2150,600)//<0,0>[`;(5)]
    \morphism(1950,200)//<0,0>[`;(6)]
    \morphism(2200,-200)//<0,0>[`;(7)]
    \morphism(2800,0)//<0,0>[`;(8)]
    \morphism(2200,-600)//<0,0>[`;(9)]
  \efig
  \end{mathpar}
  The second triangle in the proof commutes as follows: (1) and (5)--coalgebra; (2) and
  (4)--$\varepsilon$ is monoidal; (3)--$\cat{C}$ is symmetric.
  \begin{mathpar}
  \bfig
    \ptriangle|amm|/->`=`->/<600,600>[
      A\tri B`FGA\tri FGB`A\tri B;h_A\tri h_B``\varepsilon_A\tri\varepsilon_B]
    \morphism(600,0)|b|<-600,0>[FG(A\tri B)`A\tri B;\varepsilon_{A\tri B}]
    \morphism(600,600)<700,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
    \morphism(1300,0)|b|<-700,0>[F(GA\otimes GB)`FG(A\tri B);F\n{A,B}]
    \square(1300,0)/->`=`=`<-/<800,600>[
      F(GA\otimes GB)`F(GB\otimes GA)`F(GA\otimes GB)`F(GB\otimes GA);F\e{A,B}```F\e{B,A}]
    \qtriangle(2100,0)|amr|/->``->/<1400,600>[F(GB\otimes GA)`FG(B\tri A)`B\tri A;F\n{B,A}``\varepsilon_{B\tri A}]
    \morphism(2900,0)|b|<-800,0>[FGB\tri FGA`F(GB\otimes GA);\m{GB,GA}]
    \btriangle(2900,0)|mmb|/<-`=`<-/<600,400>[
      B\tri A`FGB\tri FGA`B\tri A;
      \varepsilon_B\tri\varepsilon_A``h_A\tri h_A])
    \morphism(200,500)//<0,0>[`;(1)]
    \morphism(800,300)//<0,0>[`;(2)]
    \morphism(1700,300)//<0,0>[`;(3)]
    \morphism(2500,300)//<0,0>[`;(4)]
    \morphism(3100,200)//<0,0>[`;(5)]
  \efig
  \end{mathpar}
  TODO:
  \begin{mathpar}
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\tri B)\tri C`A\tri(B\tri C)`(B\tri C)\tri A`
      (B\tri A)\tri C`B\tri(A\tri C)`B\tri(C\tri A);
      \alpha_{A,B,C}`\e{A,B\tri C}^S`\e{A,B}^S\tri id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\tri\e{A,C}^S]
  \efig
  \end{mathpar}
\end{proof}

>>>>

  \label{lem:em-ex}

@@

  The first triangle in Definition~\ref{def:smcc} commutes as follows:
  (1)--coalgebra; (2)--$\varepsilon$ is monoidal; (3)--naturality of $\rho$; (4)--naturality of
  $\varepsilon$; (5)--naturality of $\m{}$; (6)--$F$ is monoidal; (7)--$\cat{C}$ is symmetric;
  (8)--naturality of $\e{}$; (9)--$G$ is monoidal.
    \Vtriangle/->`=`/<800,800>[A\tri I'`FGA\tri FGI'`A\tri I';h_A\tri h_{I'}``]
    \Ctrianglepair(1600,0)|mmmmm|/->`<-``=`<-/<800,400>[
      FGA\tri FGI'`FGA\tri I'`FGA\tri FI`FGA\tri I';
      id_{FGA}\tri\varepsilon_{I'}`id_{FGA}\tri F\n{I'}```id_{FGA}\tri\m{I}]
    \morphism(800,400)|m|<0,-400>[FGA\tri I'`A\tri I';\varepsilon_{FGA}\tri id_{I'}]
    \morphism(1600,400)|m|<800,0>[FGA\tri FI`F(GA\otimes I);\m{GA,I}]
    \morphism(1600,0)|m|<0,-400>[FGA\tri I'`FGA;\rho_{FGA}']
    \dtriangle(1600,-400)|mmm|/->`->`<-/<800,800>[
      F(GA\otimes I)`FGA`F(I\otimes GA);
      F\rho_{GA}`F\e{GA,I}`F\lambda_{GA}]
    \square(1600,-800)/->``->`<-/<1600,1600>[
      FGA\tri FGI'`F(GA\otimes GI')`FG(I'\tri A)`F(GI'\otimes GA);
      \m{GA,GI'}``F\e{GA,GI'}`F\n{I',A}]
    \morphism(2400,400)|m|<800,400>[F(GA\otimes I)`F(GA\otimes GI');F(id_{GA}\otimes\n{I'})]
    \morphism(2400,-400)|m|<800,-400>[F(I\otimes GA)`F(GI'\otimes GA);F(\n{I'}\otimes id_{GA})]
    \morphism(0,800)|l|<0,-1200>[A\tri I'`A;\rho_A']
    \square(0,-800)|mlmb|/<-`->`<-`<-/<1600,400>[
      A`FGA`I'\tri A`FG(I'\tri A);\varepsilon_A`\lambda_A'`FG\lambda_A'`\varepsilon_{I'\tri A}]
    \morphism(800,600)//<0,0>[`;(1)]
    \morphism(1300,400)//<0,0>[`;(2)]
    \morphism(800,-200)//<0,0>[`;(3)]
    \morphism(800,-600)//<0,0>[`;(4)]
    \morphism(2150,600)//<0,0>[`;(5)]
    \morphism(1950,200)//<0,0>[`;(6)]
    \morphism(2200,-200)//<0,0>[`;(7)]
    \morphism(2800,0)//<0,0>[`;(8)]
    \morphism(2200,-600)//<0,0>[`;(9)]
  The second triangle in the proof commutes as follows: (1) and (5)--coalgebra; (2) and
  (4)--$\varepsilon$ is monoidal; (3)--$\cat{C}$ is symmetric.
    \ptriangle|amm|/->`=`->/<600,600>[
      A\tri B`FGA\tri FGB`A\tri B;h_A\tri h_B``\varepsilon_A\tri\varepsilon_B]
    \morphism(600,0)|b|<-600,0>[FG(A\tri B)`A\tri B;\varepsilon_{A\tri B}]
    \morphism(600,600)<700,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
    \morphism(1300,0)|b|<-700,0>[F(GA\otimes GB)`FG(A\tri B);F\n{A,B}]
    \square(1300,0)/->`=`=`<-/<800,600>[
      F(GA\otimes GB)`F(GB\otimes GA)`F(GA\otimes GB)`F(GB\otimes GA);F\e{A,B}```F\e{B,A}]
    \qtriangle(2100,0)|amr|/->``->/<1400,600>[F(GB\otimes GA)`FG(B\tri A)`B\tri A;F\n{B,A}``\varepsilon_{B\tri A}]
    \morphism(2900,0)|b|<-800,0>[FGB\tri FGA`F(GB\otimes GA);\m{GB,GA}]
    \btriangle(2900,0)|mmb|/<-`=`<-/<600,400>[
      B\tri A`FGB\tri FGA`B\tri A;
      \varepsilon_B\tri\varepsilon_A``h_A\tri h_A])
    \morphism(200,500)//<0,0>[`;(1)]
    \morphism(800,300)//<0,0>[`;(2)]
    \morphism(1700,300)//<0,0>[`;(3)]
    \morphism(2500,300)//<0,0>[`;(4)]
    \morphism(3100,200)//<0,0>[`;(5)]
  The third diagram commutes as follows, which uses Lemma~\ref{lem:emex}.
    \morphism(0,400)<1600,0>[(A\tri B)\tri C`A\tri(B\tri C);\alpha_{A,B,C}']
    \Vtriangle(1600,0)|amm|/->`=`->/<800,400>[
      A\tri(B\tri C)`FGA\tri FG(B\tri C)`A\tri(B\tri C);
      h_A\tri h_{B\tri C}``\varepsilon_A\tri\varepsilon_{B\tri C}]
    \morphism(800,0)|m|<-800,400>[
      FG((A\tri B)\tri C)`(A\tri B)\tri C;\varepsilon_{(A\tri B)\tri C}]
    \qtriangle(800,-400)|mmm|/`->`<-/<1600,400>[
      FG((A\tri B)\tri C)`A\tri(B\tri C)`FG(A\tri(B\tri C));
      `FG\alpha_{A,B,C}'`\varepsilon_{A\tri(B\tri C)}]
    \Ctriangle(2400,-1200)|mrm|/`->`<-/<800,800>[
      FGA\tri FG(B\tri C)`FG(A\tri(B\tri C))`F(GA\otimes G(B\tri C));
      `\m{GA,G(B\tri C)}`F\n{A,B\tri C}]
    \morphism(800,-400)<0,400>[F(G(A\tri B)\otimes GC)`FG((A\tri B)\tri C);F\n{A\tri B,C}]
    \btriangle(800,-800)|mmm|/<-``->/<1400,400>[
      F(G(A\tri B)\otimes GC)`F((GA\otimes GB)\otimes GC)`F(GA\otimes(GB\otimes GC));
      F(\n{A,B}\otimes id_{GC})``F\alpha_{GA,GB,GC}]
    \morphism(800,-800)|m|<0,-400>[
      F((GA\otimes GB)\otimes GC)`F((GB\otimes GA)\otimes GC);F(\e{A,B}\otimes id_{GC})]
    \morphism(2200,-800)|m|<1000,-400>[
      F(GA\otimes(GB\otimes GC))`F(GA\otimes G(B\tri C));F(id_{GA}\otimes\n{B,C})]
    \morphism(2200,-800)|m|<0,-400>[
      F(GA\otimes(GB\otimes GC))`F((GB\otimes GC)\otimes GA);F\e{GA,GB\otimes GC}]
    \qtriangle(2200,-1600)|mmr|/`->`->/<1000,400>[
      F((GB\otimes GC)\otimes GA)`F(GA\otimes G(B\tri C))`F(G(B\tri C)\otimes GA);
      `F(\n{B,C}\otimes id_{GA})`F\e{A,B\tri C}]
    \morphism(800,-1200)|m|<0,-400>[
      F((GB\otimes GA)\otimes GC)`F(G(B\tri A)\otimes GC);F(\n{B,A}\otimes id_{GC})]
    \morphism(2200,-1200)|m|<0,-300>[
      F((GB\otimes GC)\otimes GA)`F(GB\otimes(GC\otimes GA));F\alpha_{GB,GC,GA}]
    \morphism(800,-1200)|m|<700,-600>[
      F((GB\otimes GA)\otimes GC)`F(GB\otimes(GA\otimes GC));F\alpha]
    \morphism(2200,-1500)|m|<-700,-300>[
      F(GB\otimes(GC\otimes GA))`F(GB\otimes(GA\otimes GC));F(id_{GC}\otimes\e{C,A})]
    \morphism(800,-1600)|m|<0,-400>[F(G(B\tri A)\otimes GC)`FG((B\tri A)\tri C);F\n{B\tri A,C}]
    \morphism(2200,-1500)|m|<0,-500>[
      F(GB\otimes(GC\otimes GA))`F(GB\otimes G(C\tri A));F(id_{GB}\otimes\n{C,A})]
    \morphism(2200,-2000)|m|<0,-400>[
      F(GB\otimes G(C\tri A))`FG(B\tri(C\tri A));F\n{B,C\tri A}]
    \morphism(1500,-1800)|m|<0,-400>[
      F(GB\otimes(GA\otimes GC))`F(GB\otimes G(A\tri C));F(id_{GB}\otimes\n{A,C})]
    \morphism(1500,-2200)|m|<0,-400>[F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C));F\n{B,A\tri C}]
    \morphism(0,400)|l|<0,-2000>[(A\tri B)\tri C`(B\tri A)\tri C;\e{A,B}^S\tri id_C]
    \morphism(800,-2000)|m|<-800,400>[
      FG((B\tri A)\tri C)`(B\tri A)\tri C;\varepsilon_{(B\tri A)\tri C}]
    \morphism(0,-1600)|l|<0,-1000>[(B\tri A)\tri C`B\tri(A\tri C);\alpha_{B,A,C}']
    \morphism(1500,-2600)|m|<-1500,0>[
      FG(B\tri(A\tri C))`B\tri(A\tri C);\varepsilon_{B\tri(A\tri C)}]
    \morphism(0,-2600)|l|<0,-400>[B\tri(A\tri C)`B\tri(C\tri A);\id_B\tri\e{A,C}^S]
    \morphism(1600,-3000)|b|<-1600,0>[(B\tri C)\tri A`B\tri(C\tri A);\alpha_{B,C,A}']
    \morphism(3200,-1600)|r|<0,-1400>[
      F(G(B\tri C)\otimes GA)`FG((B\tri C)\tri A);F\n{B\tri C,A}]
    \morphism(3200,-3000)|m|<-1000,600>[FG((B\tri C)\tri A)`FG(B\tri(C\tri A));FG\alpha_{B,C,A}]
    \morphism(3200,-3000)|b|<-1600,0>[
      FG((B\tri C)\tri A)`(B\tri C)\tri A;\varepsilon_{(B\tri C)\tri A}]
